Multi-Core Model Checking and Maximum Satisfiability Applied to Hardware-Software Partitioning

### 2016-08-24 Docs/IJES/journal.tex
revised version

This article is organized as follows: Section~\ref{background} gives a background on optimization techniques, $\nu$Z, ESBMC, and OpenMP tools. 
Section~\ref{Mathematical-modeling} describes the informal and formal mathematical modeling. The SMT-based BMC method is presented in Section~\ref{Analysis-of-the-partitioning-problem-using-ESBMC}, and in particular, Section~\ref{Analysis-of-the-partitioning-problem-using-vZ} presents the partitioning model using $\nu$Z. In Section~\ref{Experimental-Evaluation}, we show the experimental results using several embedded systems applications. In Section~\ref{Related-Work}, we discuss the related work and we conclude and describe future work in Section~\ref{Conclusions}.

@@

\vspace{2 mm}
Here can be cited the relevant work of ~\cite{Mann2007} in optimization, who modified a branch-and-bound algorithm to speed up the execution time. ~\cite{Sapienza2013} used multiple criteria decision analysis to solve the HW-SW partitioning problem.

In some cases, the time to find a solution using ILP is impractical. Even with the use of powerful computers, a problem can take hours before an optimal solution is reached. If the optimization problem is complex, some heuristics can be used to solve the same problem faster, as described by~\cite{Rao2009}, {\it e.g.}, those used in the GA. The only drawback is that the found solution may not be the global minimum or maximum. As relevant works, ~\cite{Jiang2012} used a GA mixed with simulated annealing. And~\cite{Huong2012} designed a Pareto optimization modified using GA.

@@

The clustering benchmark seems to be the limit to test the ESBMC (described) implementations; note, however, that more than $150$ nodes lead to TO and MO. ILP shows robustness and produces results even for a high number of nodes and edges, but limited to $329$ nodes.

@@

Finally, there is an issue about $150$ nodes problem, since it seems to be the limit of multi-core ESBMC. However, it really depends on the modeling granularity of the problem. Some researchers propose fine-grained models, in which each instruction can be mapped to either HW or SW. This may lead to thousands of nodes or even more. Others defend coarse-grained models, where decisions are made for larger components, thus even complex systems may consist of just some dozens of nodes to partition. In principle, a fine-grained approach may allow to obtain better partitions, but at the cost of an exponential increase of the search space size. In future work, we will address improvements in ESBMC to remove the parallel layer on top of ESBMC and implement it during symbolic execution so that we can optimize the overall verification time. \textcolor{blue}{Moreover, it will address specifically more complex types of architectures of HW-SW model, including more than one CPU, and the assumption of just singled-threaded program execution
will be extended to multiprogramming and multiprocessing (second generation of co-design).}

>>>>

This article is organized as follows: Section~\ref{background} gives a background on optimization techniques, $\nu$Z, ESBMC, and OpenMP tools. 
Section~\ref{Mathematical-modeling} describes the informal and formal mathematical modeling. The SMT-based BMC method is presented in Section~\ref{Analysis-of-the-partitioning-problem-using-ESBMC}, and in particular, Section~\ref{Analysis-of-the-partitioning-problem-using-vZ} presents the partitioning model using $\nu$Z. In Section~\ref{Experimental-Evaluation}, we show the experimental results using several embedded systems applications. And we conclude and describe future work in Section~\ref{Conclusions}.

@@

\vspace{2 mm}
\textcolor{blue}{Here can be cited the relevant work of ~\cite{Mann2007} in optimization, who modified a branch-and-bound algorithm to speed up the execution time. ~\cite{Sapienza2013} used multiple criteria decision analysis to solve the HW-SW partitioning problem.}

In some cases, the time to find a solution using ILP is impractical. Even with the use of powerful computers, a problem can take hours before an optimal solution is reached. If the optimization problem is complex, some heuristics can be used to solve the same problem faster, as described by~\cite{Rao2009}, {\it e.g.}, those used in the GA. The only drawback is that the found solution may not be the global minimum or maximum. \textcolor{blue}{As relevant works, ~\cite{Jiang2012} used a GA mixed with simulated annealing. And~\cite{Huong2012} designed a Pareto optimization modified using GA.}

@@

The clustering benchmark seems to be the limit to test the ESBMC (described) implementations; 
\textcolor{blue}{although more benchmarks with complexity similar to clustering should be included in future work for a more precise conclusion. Note, however, that more than $150$ nodes lead to TO and MO. ILP shows robustness and produces results even for a high number of nodes and edges, but limited to RC$6$ benchmark with $329$ nodes.}

@@

Finally, there is an issue about $150$ nodes problem, since it seems to be the limit of multi-core ESBMC. However, it really depends on the modeling granularity of the problem. Some researchers propose fine-grained models, in which each instruction can be mapped to either HW or SW. This may lead to thousands of nodes or even more. Others defend coarse-grained models, where decisions are made for larger components, thus even complex systems may consist of just some dozens of nodes to partition. In principle, a fine-grained approach may allow to obtain better partitions, but at the cost of an exponential increase of the search space size.

In future work, we will address improvements in ESBMC to remove the parallel layer on top of ESBMC and implement it during symbolic execution so that we can optimize the overall verification time. \textcolor{blue}{And so that the limits of the techniques can be defined more precisely, new benchmarks will be included in future work, with their complexity ranging between 100 and 400 nodes. Furthermore, more complex types of architectures of HW-SW model will be addressed, including more than one CPU, and the assumption of just singled-threaded program execution will be extended to multiprogramming and multiprocessing (second generation of co-design).}
